---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard
    
---

```{r}
library(tidyverse)
library(ggplot2)
library(plotly)
library(knitr)
df <- read_csv('https://bryantstats.github.io/math421/data/titanic.csv')
df <- df %>% 
  mutate(Survived = as.character(Survived),
         Pclass = as.character(Pclass))
```


Visualizations {data-icon= "icon-social-twitter"}
===================================== 
    
{data-width=350}
-----------------------------------------------------------------------

### Row 1
    
```{r}
p <- df %>% ggplot() + geom_point(aes(x=Age, y=Fare, color = Survived))
ggplotly(p)
```

### Row 2

- Is it working?

Column {data-width=350}
-----------------------------------------------------------------------

### Row 3

```{r}
p
```

### Row 4

```{r}
p
```


### Row 5

```{r}
p
```



Tables {data-icon="fa-table"}
=====================================     

### Table 1

Row {}
-----------------------------------------------------------------------

```{r}
df %>% select(Survived, Sex) %>% head(10) %>% kable
```

Row {}
-----------------------------------------------------------------------

- The midterm has two components: the Rmarkdown notebook (html) and the presentation. We will do the presentation in class. Post both the notebook and the presentation on your Github page.

Tables
=====================================
    
### Table 2

#### Checking

- The midterm has two components: the Rmarkdown notebook (html) and the presentation. We will do the presentation in class. Post both the notebook and the presentation on your Github page.

- The notebook: The notebook should be created using rmarkdown (like other assignments). The notebook should have a title. It should have a table of content (TOC form) or in a tab form. The Rmd files of Tab and Toc form are available on the class webpage.

- The Presentation: Present your results in 5-10 minutes. To make the presentation using Rmarkdown, do the follows:


