---
title: "R Basics"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
   

---
# R as a calculator

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```


```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r, echo=FALSE}
xaringanExtra::use_webcam()
```

```{r xaringan-fit-screen, echo=FALSE}
xaringanExtra::use_fit_screen()
```

- Addition: +

- Subtraction: -

- Multiplication: *

- Division: /

- Exponentiation: ^

--

Put the following to the console in Rstudio

```{r}
(3+4)^2 - 3^4 - 1/2 - 3*4
```


---
# Data structures in R

|    | Homogeneous | Heterogeneous |
|----|-------------|---------------|
| 1d | Vector      | List          |
| 2d | Matrix      | Data Frame    |
| nd | Array       |               |


---
# Vector

- Numeric vectors
```{r}
x <- c(2,3,4,5,6)
x
```

- Use `<-` to assign *something* to a variable/an object

---
# Vector

- Character vectors
```{r}
x <-  c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
x
```

--

- Logical vectors

```{r}
x <- c(TRUE, FALSE, TRUE)
sum(x)
```

---
# Operations on Numeric Vectors

- Operations on Vectors are **element-to-element**

- You can add, subtract, multiply, and divide vectors

--

```{r}
x <- c(2, 3, 4, 5, 6)
y <- c(1, 0, 0, 0, 99)
x+y
x-y
x*y
```



---
# Operations on Numeric Vectors

- You can apply a function to vector
```{r}
x <- c(2, 3, 4, 5, 6)
y <- c(1, 0, 0, 0, 99)
x^2
log(x)
sin(x)
```



---
# Some functions with vectors

```{r}
x <- c(2, 3, 40, 5, 6)
mean(x)
sum(x)
max(x)
length(x)
```

---
# Some functions with vectors

```{r}
x <- c(2, 3, 40, 5, 6)
# Standard Deviation
sd(x)
# Index of the maximum element
which.max(x)

# Index of the element equaling 40
which(x==40)

```


---
# Quickly generate vectors

```{r}
c(1:10)

rep(1, 10)

rep(c(1,2,3), 10)

# Arithmetic sequences
seq(1, 2, .2)

```


---
class: inverse, middle, center

# Live Coding 

solve problems, (talk about variable environment, variables, shortcuts...) 

present the results in an rmarkdown and 

publish it to Github Page




---
class:inverse
# Problem

- **Calculate**: 
$$
S_{1} = 1 + 2 +...+  100
$$
--

- **Solution**
```{r}
x <- c(1:100)

sum(x)
```

---
class:inverse
# Problem

- **Calculate**
$$
S_{2} = 1^2 + 2^2 +...+  100^2
$$
--

- **Solution**

```{r}
x <- c(1:100)
sum(x^2)

```

---
class:inverse
# Problem

- **Calculate**
$$
S = \frac{1^3 + 2^3 +...+  100^3}{100}
$$
--

- Solution*

```{r}
x <- c(1:100)
sum(x^3)/100

```

--

- **Another way?**

--

```{r}
# Or

mean(x^3)
```


---
class:inverse
# Problem

- **Calculate**
$$
S = 1\cdot 2 + 3 \cdot 4 + 5 \cdot 6 + 7 \cdot 8 +...+ 99 \cdot 100
$$
--


- **Solution**

```{r}
x <- seq(1, 99, 2)
y <- seq(2, 100, 2)

sum(x*y)

```

---
class:inverse
# Problem

- **Calculate**
$$
S = \frac{1}{2} + \frac{2}{3} + \frac{3}{4} + ...+  \frac{100}{101}
$$
--


- **Solution**

```{r}
x <- c(1:100)
y <- c(2:101)

sum(x/y)

```

---
class:inverse
# Problem

- Is this summation *convergent* or *divergent*?

$$
S = 1+\frac{1}{4}+\frac{1}{9}+\frac{1}{16}+\frac{1}{25}+...
$$


---
class:inverse
# Solution

- Rewrite $S$:

$$
S = 1+\frac{1}{2^2}+\frac{1}{3^2}+\frac{1}{4^2}+\frac{1}{5^2}+...
$$
--

- The sum of the first 1000 terms

```{r}
n <-  1000
x <-  c(1:n)
sum(1/x^2)
```
--

- The sum of the first 10000 terms

```{r}
n <-  10000
x <-  c(1:n)
sum(1/x^2)
```

---
class: center, middle, inverse

### The series converges! 

---
class: center, middle, inverse

### YOUR TURN

This is also your assignment 2:https://bryantstats.github.io/math421/assignments/assignment2.html

---
class:inverse
# Problem

***Guideline***: Use the rmarkdown [here](https://bryantstats.github.io/math421/assignments/assignment2.Rmd) as a template to write your codes. Open the Rmarkdown file in Rstudio. After each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the questions. `Knit` the rmarkdown file (hotkey `Ctrl + Alt + K`) to export an html.  Then Publish the html to your Githiub Page. 

***Submissions***: Submit the link on Github of the assignment to Blackboard under Assignment 2. 

**Go the the next page for the problems**

---
class:inverse
# Problem

- **Calculate**

$$
S = 1 + 4 + 7 + 11+... + 100
$$
$$
S = 1^{100} + 2^{100} + 3^{100} +...+100^{100}
$$
$$
S = \frac{1}{1\cdot 2}+\frac{1}{2 \cdot 3}+...+\frac{1}{100\cdot 101}
$$

$$
S = \frac{1}{1\cdot 2 \cdot 3}+\frac{1}{2 \cdot 3 \cdot 4}+...+\frac{1}{100\cdot 101 \cdot 102}
$$

$$
S = 1^1 + 3^3 + 5^5 + 7^7 +....+101^{101}
$$


