
---
title: "Visualization - Aesthetic Mapping - Titanic - Plotly"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      
---
class: inverse, middle, center

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```


```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r, echo=FALSE}
xaringanExtra::use_webcam()
```

```{r xaringan-fit-screen, echo=FALSE}
xaringanExtra::use_fit_screen()
```
---

```{r}
library(tidyverse)
library(ggplot2)
library(plotly)
df <- read_csv('https://bryantstats.github.io/math421/data/titanic.csv')
df <- df %>% 
  mutate(Survived = as.character(Survived),
         Pclass = as.character(Pclass))
```


---
```{r}
df %>% ggplot()+
  geom_density(mapping = aes(x = Age, color=Survived))
```

---
```{r}
p <- df %>% ggplot()+
  geom_density(mapping = aes(x = Age, color=Survived))
ggplotly(p)
```

---
**One Continuous Variable: Density**

```{r}
df %>% ggplot()+
  geom_density(mapping = aes(x = Age))
```

---
**One Continuous Variable: Density**

```{r}
p <- df %>% ggplot()+
  geom_density(mapping = aes(x = Age))
ggplotly(p)

```

---
**One Continuous Variable: Histogram**

```{r}
df %>% ggplot()+
  geom_histogram(mapping = aes(x = Age))
```

---
**One Continuous Variable: Histogram**

```{r}
p <- df %>% ggplot()+
  geom_histogram(mapping = aes(x = Age))
ggplotly(p)
```


---
**One Categorical Variable: Bar chart**

```{r}
df %>% ggplot()+
  geom_bar(mapping = aes(x = Survived))
```

---
**One Categorical Variable: Bar chart**

```{r}
p <- df %>% ggplot()+
  geom_bar(mapping = aes(x = Survived))
ggplotly(p)
```

---
**Two numeric: Scatter Plot: `geom_point`**

```{r}
df %>% ggplot()+geom_point(aes(x=Age, y=Fare))
```


```{r}
p <- df %>% ggplot()+geom_point(aes(x=Age, y=Fare))
ggplotly(p)
```

---
**Two numeric: Line Plot: `geom_line`**

```{r}
df %>% ggplot()+geom_line(aes(x=Age, y=Fare))
```


---
**Two numeric: Line Plot: `geom_line`**

```{r}
p <- df %>% ggplot()+geom_line(aes(x=Age, y=Fare))
ggplotly(p)
```

---
**Two numeric: Smooth Plot: `geom_smooth`**

```{r}
df %>% ggplot()+geom_smooth(aes(x=Age, y=Fare))
```

---
**Two numeric: Smooth Plot: `geom_smooth`**

```{r}
p <- df %>% ggplot()+geom_smooth(aes(x=Age, y=Fare))
ggplotly(p)
```

---
**Two numeric: geom_point + geom_smooth**

```{r}
df %>% ggplot() + geom_point(aes(x=Age, y=Fare))+
  geom_smooth(aes(x=Age, y=Fare))
```

---
**Two numeric: geom_point + geom_smooth**

```{r}
p <- df %>% ggplot() + geom_point(aes(x=Age, y=Fare))+
  geom_smooth(aes(x=Age, y=Fare))
ggplotly(p)
```


---
**One Continuous + One Categorical: Density**

```{r}
df %>% ggplot()+
  geom_density(mapping = aes(x = Age, color = Survived))
```

---
**One Continuous + One Categorical: Density**

```{r}
p <- df %>% ggplot()+
  geom_density(mapping = aes(x = Age, color = Survived))
ggplotly(p)
```


---
**One Continuous + One Categorical: Boxplot**

```{r}
df %>% ggplot()+
  geom_boxplot(mapping = aes(x = Age, y = Survived))
```

---
**One Continuous + One Categorical: Boxplot**

```{r}
p <- df %>% ggplot()+
  geom_boxplot(mapping = aes(x = Age, y = Survived))
ggplotly(p)
```


---
**Two categorical variables: Barplot**

```{r}
df %>% ggplot()+
  geom_bar(mapping=aes(x=Sex, fill=Survived), position = 'fill')
```


---
**Two categorical variables: Barplot**

```{r}
p <- df %>% ggplot()+
  geom_bar(mapping=aes(x=Sex, fill=Survived), position = 'fill')
ggplotly(p)
```

---
** Three variables**

```{r}
df %>% ggplot() + geom_point(aes(x=Age, y=Fare, color = Survived))
```

---
** Three variables**

```{r}
p <- df %>% ggplot() + geom_point(aes(x=Age, y=Fare, color = Survived))
ggplotly(p)
```

