
---
title: "Visualization - Aesthetic Mapping - Titanic"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      
---
class: inverse, middle, center

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```


```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r, echo=FALSE}
xaringanExtra::use_webcam()
```

```{r xaringan-fit-screen, echo=FALSE}
xaringanExtra::use_fit_screen()
```
---
# A visualization:

--

- is a geometry object (a geom)

--

- whose aesthetics

--

- represents variables

--

- from a data set


---
# Aesthetics mean

--

- “something you can see”. 

--

Examples include:

- position (i.e., on the x and y axes)
- color (“outside” color)
- fill (“inside” color)
- shape (of points)
- size

---
# Aesthetics Mapping

--

- map

--

- variables

--

- to aesthetics

---
class: inverse, middle, center
# Examples

---

```{r}
library(tidyverse)
library(ggplot2)
df <- read_csv('../data/titanic.csv')
df <- df %>% 
  mutate(Survived = as.character(Survived),
         Pclass = as.character(Pclass))
```


---
```{r}
df %>% ggplot()+
  geom_density(mapping = aes(x = Age, color=Survived))
```
---
# Aesthetic of a geom

- A geom has its list of own aesthetics

- Use `?geom_point()` to check for the list of `geom_point`

- Some aesthetics are required, some are not

---
class: inverse, middle, center
# Common Visualization Practices

---
# One Continuous Variable

- Density: `geom_density`

- Histogram: `geom_histogram`

- Boxplot: `geom_boxplot`

---
**One Continuous Variable: Density**

```{r}
df %>% ggplot()+
  geom_density(mapping = aes(x = Age))
```

---
**One Continuous Variable: Histogram**

```{r}
df %>% ggplot()+
  geom_histogram(mapping = aes(x = Age))
```


---
**One Categorical Variable: Bar chart**

```{r}
df %>% ggplot()+
  geom_bar(mapping = aes(x = Survived))
```

---
# Two Continuous Variables

- Scatter Plot: `geom_point`
- Line Plot: `geom_line`
- Smooth Plot: `geom_smooth`


---
**Two numeric: Scatter Plot: `geom_point`**

```{r}
df %>% ggplot()+geom_point(aes(x=Age, y=Fare))
```


---
**Two numeric: Line Plot: `geom_line`**

```{r}
df %>% ggplot()+geom_line(aes(x=Age, y=Fare))
```


---
**Two numeric: Smooth Plot: `geom_smooth`**

```{r}
df %>% ggplot()+geom_smooth(aes(x=Age, y=Fare))
```

---
**Two numeric: geom_point + geom_smooth**

```{r}
df %>% ggplot() + geom_point(aes(x=Age, y=Fare))+
  geom_smooth(aes(x=Age, y=Fare))
```


---
# One Continuous Variable + One Categorical Variable

- Density
- BoxPlot

---
**One Continuous + One Categorical: Density**

```{r}
df %>% ggplot()+
  geom_density(mapping = aes(x = Age, color = Survived))
```

---
**One Continuous + One Categorical: Boxplot**

```{r}
df %>% ggplot()+
  geom_boxplot(mapping = aes(x = Age, y = Survived))
```
---
# Two categorical variables

- Barplot

---
**Two categorical variables: Barplot**

```{r}
df %>% ggplot()+
  geom_bar(mapping=aes(x=Sex, fill=Survived), position = 'fill')
```

---
** Three variables**

```{r}
df %>% ggplot() + geom_point(aes(x=Age, y=Fare, color = Survived))
```

---
# More

- [ggplot cheat sheet](https://raw.githubusercontent.com/rstudio/cheatsheets/main/data-visualization.pdf)

