
---
title: "Tidymodels"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: united
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Step 1: Data Partition


```{r}
library(tidyverse)
library(tidymodels)
df <- read_csv('https://bryantstats.github.io/math421/data/titanic.csv')

df <- df %>% rename(target=Survived)

set.seed(123)
split <- initial_split(df, prop = 0.80, strata = target)
df_train <- training(split)
df_test <- testing(split)
```



-------

## Step 2:

```{r}
# preprocessing
df_recipe <- 
  recipe(target ~ ., 
         data = df_train) %>% # keep variables we want
  step_impute_median(Age,Fare) %>% # imputation
  step_impute_mode(Embarked) %>% # imputation
  step_mutate_at(target, Pclass, Sex, Embarked, fn = factor) %>% # make these factors
  step_mutate(Travelers = SibSp + Parch + 1) %>% # new variable
  step_rm(SibSp, Parch, Cabin) %>% # remove variables
  step_dummy(all_nominal_predictors()) %>% # create indicator variables
  step_normalize(all_numeric_predictors()) # normalize numerical variables
```

-------

## II. Data Visualization

Continue with the data from part I. 

1. Provides at least 10 meaningful plots. Comments on the plots. All plots should have title, caption, appropriate labels on x and y-axis

2. Make an animation plot. 

3. Write a paragraph to summarize the section and give your comments on the results. 

-------

## III. Predictive Models

Continue with the data from part I. Make sure you do not have any missing values in the data. Use the follows as the target and input variables: 

*Target Variable*: Create the target variable taking value of 

  - `low` if the total charge of a patient (`tot`) is smaller than the median of the total charge, and

  - `high` otherwise. 

*Input Variables*:

  - "age","sex","raceethn","provider","moa","mod","admtype","campus", 'los'
  
-------

1. Use `filter` function to filter out rows where `raceethn==''` or `admtype==''`. Make sure all the categorical variables are factor, numeric variables are numeric. Set Training : Testing Split = 10 : 90 

2. Train a decision tree using `rpart`.  Plot the decision tree. Plot the variable importance ranked by the tree. 

3. Using caret for this question. Set `Training Control` to be: Use Cross-Validation of 5 folds across all models.  Train & tune at least 2 different models (i.e. two different values for `method=` in the train function of caret).  Plot the hyper-parameter tuning plots for each model. 

4. Plot the comparison of the models in 3. 

5. What is your final selection for the model? Test the accuracy of your final model on the test data. 

6. Create another `target` variable (binary), decide the input variables and redo 1 to 5. 

7. Write a paragraph to summarize the section and give your comments on the results. 

-------