
---
output: # rmarkdown::github_document
  html_document:
    theme: cerulean
    toc: true
  pdf_document: default
  word_document: default
title: "Assignment 5: Handle Missing Values"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment5.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 5. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

**The data:** 

This assignment works with the Adult Census Data that can be downloaded at [this link.](https://bryantstats.github.io/math421/data/adult_census_missing.csv)

-------

**Questions**

1. Use read_csv to import the data.  Show the number of missing values (NA) for each columns.   

-------

2. Using function `aggr` the VIM package to plot the number of missing values for each column. 

-------

3. Find 

-------

4.  Create a dataset where the rows with missing data are removed. The original dataset remains unchanged by this action.

-------

5.  Replace the missing values of numeric variables with the corresponding average of the columns.


-------

6.  Replace the missing values of categorical variables with the corresponding mode (most frequent value) of the columns. Hint:  You can use the `table` function to see what is the mode of the variable. 

-------

7.  The `Survived` column records whether a passenger is survived or not. `Survived = 1` means the passenger survived. Thus, the chance of survived for a random passenger can be estimated by

```{r, eval=FALSE}
mean(df$Survived)
```

Compare the chance of survived between male and female.  *Hint (Use group_by + summarise combo)*

-------

8.  Use the `summary` function to find the first quartile (Q1) and the thrid quartile(Q3) of variable `Age`. Create a new variable taking values of `young` (Age < Q1), `middle` (Age from Q1 to Q3), and `old`(Age > Q3). Compare the chance of survived between these three groups of age. 

-------

9.  This dataset ([link](data/Vehicle.CSV)) records the vehicles in car accident in 2019. The variable information can be found at [this link.](data/Fatality Analysis Reporting System (FARS) Analytical User’s Manual, 1975-2019.pdf) Import the data using `read_csv`. Let `d` be the data containing only accidents happened in Rhode Island.  Is there any missing values in `d`? 

-------

10. Continue with the dataset `d` in Question 9. We will analyze the traveling speed variable (`TRAV_SP`). This variable records the travel speeds (miles per hours) when the accident happened. Use the `table` function to check all the values of this variable.  Do you observe any unexpected values?  These unexpected values are actually the codes for missing values.  Use the `na_if` function to changes the unexpected values to `NA`.  Then replace the NAs by the average speed. 

